### 2016-03-21 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Include more figures into CH03

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of an $F$ distribution with $n_{i-1}$ and $n_{i}$ degrees of freedom.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\begin{figure}[tbh]
\centering
\remakeNextFigure
 \setlength\figurewidth{0.8\columnwidth}
 \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/truncRMS.tikz}
\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response. The different segments are separated by dotted lines.}
\label{fig:nonparametric:truncation:Ftest}
\end{figure}

@@

\begin{figure}[tbh] %top bottom here
    \centering
    \setlength\figurewidth{0.85\columnwidth}
    \setlength\figureheight{0.68\figurewidth}

@@

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
        \setlength\figurewidth{0.85\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/pdfs.tikz}
         \caption[RMS error of the FRF versus truncation time.]{
         The left y-axis shows the \gls{RMS} error of the estimated \gls{FRF} as a function of the chosen truncation time $\truncTime$.
         The corresponding optimal $\truncTime$ is indicated as well.
         Both bar plots (right y-axis) indicate for $\nMC =1000$ realizations of the disturbing noise and excitation signal, the number of times that $\truncTime$ has been selected by means of either the method using the $F$-test or the method that fits an exponential.
         It can be seen that both methods allow to almost halve the \gls{RMS} error and approach the optimal truncation time.}
   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

@@

>>>>

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise, the null hypothesis states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\begin{figure}[tbh]
\centering
 \setlength\figurewidth{0.8\columnwidth}
 \setlength\figureheight{0.68\figurewidth}
  \input{\thisDir/figs/truncRMS.tikz}
\caption[Illustration of impulse response truncation using the $F$-test.]{Illustration of truncating the impulse response by performing an $F$-test on successive segments of the impulse response. The different segments are separated by dotted lines.}
\label{fig:nonparametric:truncation:Ftest}
\end{figure}

@@

\begin{figure}[tbh] %top bottom here
    \centering
    \setlength\figurewidth{0.85\columnwidth}
    \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/figLPMvsTrunc.tikz}

@@

\begin{figure}
   \centering
   \remakeNextFigure
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/pdfs.tikz}
         \caption[RMS error of the FRF versus truncation time.]{
         The left y-axis shows the \gls{RMS} error of the estimated \gls{FRF} as a function of the chosen truncation time $\truncTime$.
         The corresponding optimal $\truncTime$ is indicated as well.
         Both bar plots (right y-axis) indicate for $\nMC =1000$ realizations of the disturbing noise and excitation signal, the number of times that $\truncTime$ has been selected by means of either the method using the $F$-test or the method that fits an exponential.
         It can be seen that both methods allow to almost halve the \gls{RMS} error and approach the optimal truncation time.}
   \label{fig:pdfAndRMSeVStruncTime}
\end{figure}

@@

\TODO{write about boxcar average, add reference}
\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of a boxcar averager}
\end{figure}

\TODO{RMSE vs $\truncTime$ for boxcar figure}
